Manuscript title here

### 2024-09-16 manuscript.Rmd
Fortsättning på metod, väntar på svar hur man använder ATLS kliniskt.

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate, bloodpressure, respiratory rate and mental status. Based on these four measurements, the patients will be classified into four groups rouphly based on the same value as in the ATLS trauma shock classifications. <!-- Elaborate on how you will categorise the degree of shock, what are the different levels?--> The outcome will be OFI recorded in the trauma care quality database and are binary when used to calculate the association with degree of shock. The subgroups of OFI will be explored and reported in a list, and therefore non-binary.

@@

Size of the data.<!-- Mention that you will include all available data-->

@@

>>>>

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate(HR), blood pressure(BP), respiratory rate(RR) and mental status. Based on these four measurements, the patients will be classified into four groups roughly based on the same value as in the ATLS trauma shock classifications.

<!-- Elaborate on how you will categorise the degree of shock, what are the different levels?-->
The first group will be patients presenting with a HR below 100 beats per minute(BPM), respiratory rate between 14 to 20. The original ATLS classification only states normal BP, but no number. In our case, we will be using the systolic over 90mmhg as the lower limit up to 65 years old, and 110mmhg as the lower limit for patients older (geriatric patients). The...

The outcome will be OFI recorded in the trauma care quality database and are binary when used to calculate the association with degree of shock. The subgroups of OFI will be explored and reported in a list, and therefore non-binary.

@@

All available data in the trauma care quality database? will be included, regarding the studied variables. <!-- Mention that you will include all available data-->

@@

I will be using R to...
